Data_Analysis_exp7

### 2017-12-30 Traditional_Analysis/Analysis_exp7_2.rmd
revise code again

lapply(pkgNeeded,pkgTest)
rm(pkgNeeded)
# using APA style plot
# Save some time and stor APA format-related code in an object so you can easily
# use it in multiple plots
windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
apatheme=theme_bw()+
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              text=element_text(family='Times'),
              legend.title=element_blank(),
              legend.position='top',
              axis.line.x = element_line(color='black'),
              axis.line.y = element_line(color='black'))

@@

        datac <- rename(datac,c("mean" = measurevar))

@@

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L
df.T1 <- df.T
df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000

@@

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_L, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
## calculate the d prime for each condition
# calculate the number of hit,CR,miss or FA 
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "FA"
        }
}

@@

# summary(aov(dprime ~ Morality*Identity + Error(Subject/(Morality*Identity)), data=df.L1.V.SDT_w))
df.L1.V.SDT_w$Subject <- factor(df.L1.V.SDT_w$Subject)
e7_L.dprime_anova_bf = anovaBF(dprime ~ Morality*Identity + Subject, data = df.L1.V.SDT_w, whichRandom = "Subject")

# Good self vs Bad self
e7_L.d.t.good_bad_slf <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Self_Bad,paired = TRUE)
df.L1.V.SDT_ww$good_bad_slf <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Self_Bad
e7_L.d.t.good_bad_slf.CI <- bootES(df.L1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d")

e7_L.d.tvalue.good_bad_slf <- round(as.numeric(e7_L.d.t.good_bad_slf[[1]]),3)
e7_L.d.df.L1.good_bad_slf <- as.numeric(e7_L.d.t.good_bad_slf[[2]])
e7_L.d.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_slf[[3]]),"bonferroni",4)
e7_L.d.cohens.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[1]],4) 
e7_L.d.CI.L.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][1],4)
e7_L.d.CI.H.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][2],4)

@@

#####save the dprime and ACC data for late used####
colnames(df.L1.V.SDT_ww) <- paste("L_d", colnames(df.L1.V.SDT_ww), sep = "_")
write.csv(df.L1.V.SDT_ww,"data_matching_v_dprime.csv",row.names=FALSE)
df.L1.V.acc <-  ddply(df.L1.V,.(Subject,Match,Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))
df.L1.V.acc_w <- dcast(df.L1.V.acc, Subject ~ Match + Identity + Morality ,value.var = "ACC")
df.L1.V.acc_w$good_bad_slf <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Self_Bad
df.L1.V.acc_w$good_oth <- df.L1.V.acc_w$match_Other_Good - df.L1.V.acc_w$match_Other_Bad
df.L1.V.acc_w$slf_oth_good <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Other_Good
df.L1.V.acc_w$slf_oth_bad <- df.L1.V.acc_w$match_Self_Bad - df.L1.V.acc_w$match_Other_Bad

colnames(df.L1.V.acc_w) <- paste("L_acc", colnames(df.L1.V.acc_w), sep = "_")
colnames(df.L1.V.acc_w)[colnames(df.L1.V.acc_w) == 'L_acc_Subject'] <- 'Subject'
write.csv(df.L1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
#####

@@

e7_L.p_dprime1 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3,width = .6) +    # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'self-referential',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme

e7_L.p_dprime2 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme + 
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other"))+
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("e7_L.p_dprime2.pdf", e7_L.p_dprime2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
# tiff(filename = "e7_L.p_dprime2.tiff", width = 8, height = 8, units = 'in', res = 300)
# e7_L.p_dprime2
# dev.off()

@@

```{r plot1 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'self-referential',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme

# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
```

@@

```{r plot2 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme

# ggsave('dprime_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot
```

@@

##### save the rt data for late used ####
colnames(df.L1.V.RT.subj_w) <- paste("L_rt", colnames(df.L1.V.RT.subj_w), sep = "_")
colnames(df.L1.V.RT.subj_w)[colnames(df.L1.V.RT.subj_w) == 'L_rt_Subject'] <- 'Subject'
write.csv(df.L1.V.RT.subj_w,"data_matching_v_RT.csv",row.names=FALSE)
#### save the rt data ###

@@

e7_L.p_rt1 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Self-referential") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times (ms)") + 
        apatheme

e7_L.p_rt2 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +   # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Moral valence") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800))+
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) +
        scale_y_continuous("Reation Times  (ms)",breaks = seq(500,800,50),expand = c(0, 0)) +
        apatheme + 
        theme(axis.text = element_text (size = 24)) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("e7_L.p_rt2.pdf", e7_L.p_rt2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")
#tiff(filename = "e7_L.p_rt2.tiff", width = 8, height = 8, units = 'in', res = 300)
#e7_L.p_rt2
#dev.off()

#tiff(filename = "Figure exp7. d prime and RTs of Experiment 7 (way 2).tiff", width = 8, height = 6, units = 'in', res = 300)
#multiplot(e7_L.p_dprime2,e7_L.p_rt2,cols = 2)
#dev.off()

@@

```{r plot2 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
# change a way to plot
ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Self-referential") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times (ms)") + 
        apatheme
#ggsave('RT_mean_plot2.png', width=4, height=6, unit='in', dpi=300)  # save the plot

@@

```{r plot1 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
# df.L1.V.RT.grand.match <- df.L1.V.RT.grand[df.L1.V.RT.grand$Matchness == "match",]
ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = .3,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Moral valence") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800))+
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) + 
        apatheme
#ggsave('RT_mean_plot.png', width=4, height=6, unit='in', dpi=300)  # save the plot

>>>>

lapply(pkgNeeded,pkgTest) # please pay attention to the overlap between differen libraries.
rm(pkgNeeded)             # remove the pkgNeeded variable

# using APA style plot for later use
windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
apatheme=theme_bw()+
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              text=element_text(family='Times'),
              legend.title=element_blank(),
              legend.position='top',
              axis.line.x = element_line(color='black'),
              axis.line.y = element_line(color='black'))

@@

        datac <- plyr::rename(datac,c("mean" = measurevar))

@@

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L
df.T1 <- df.T
df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

@@

### Results of Learning phase
#### Analaysis of d prime
```{r analyzing for d prime_e7_match, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
## calculate the d prime for each condition
# calculate the number of hit,CR,miss or FA 
df.L1.V$sdt <- NA
for (i in 1:nrow(df.L1.V)){
        if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "hit"
        } else if (df.L1.V$ACC[i] == 1 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "CR"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "match" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "miss"
        } else if (df.L1.V$ACC[i] == 0 & df.L1.V$Match[i] == "nonmatch" & !is.na(df.L1.V$ResponseKey[i])){
                df.L1.V$sdt[i] <- "FA"
        }
}

@@

df.L1.V.SDT_w$Subject <- factor(df.L1.V.SDT_w$Subject)  # make the subject "factor"

# using Bayesfactor analysis (which is not reported in the document)
e7_L.dprime_anova_bf  <- anovaBF(dprime ~ Morality*Identity + Subject, data = df.L1.V.SDT_w, whichRandom = "Subject")

# Good self vs Bad self
e7_L.d.t.good_bad_slf <- t.test(df.L1.V.SDT_ww$Self_Good,df.L1.V.SDT_ww$Self_Bad,paired = TRUE)     # t-test
df.L1.V.SDT_ww$good_bad_slf <- df.L1.V.SDT_ww$Self_Good - df.L1.V.SDT_ww$Self_Bad                   # calculate the differences
e7_L.d.t.good_bad_slf.CI <- bootES(df.L1.V.SDT_ww$good_bad_slf,R = 20000, effect.type = "cohens.d") # calculate the cI using BootES

# give new names for each key information, for later use in the markdown
e7_L.d.tvalue.good_bad_slf <- round(as.numeric(e7_L.d.t.good_bad_slf[[1]]),3)
e7_L.d.df.L1.good_bad_slf <- as.numeric(e7_L.d.t.good_bad_slf[[2]])
e7_L.d.pvalue.good_bad_slf.adj <- p.adjust(as.numeric(e7_L.d.t.good_bad_slf[[3]]),"bonferroni",4)
e7_L.d.cohens.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[1]],4) 
e7_L.d.CI.L.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][1],4)
e7_L.d.CI.H.good_bad_slf <- round(e7_L.d.t.good_bad_slf.CI[[12]][2],4)

@@

#####save the dprime and ACC data for late used ####
colnames(df.L1.V.SDT_ww) <- paste("L_d", colnames(df.L1.V.SDT_ww), sep = "_")
write.csv(df.L1.V.SDT_ww,"data_matching_v_dprime.csv",row.names=FALSE)
df.L1.V.acc <-  ddply(df.L1.V,.(Subject,Match,Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))
df.L1.V.acc_w <- dcast(df.L1.V.acc, Subject ~ Match + Identity + Morality ,value.var = "ACC")
df.L1.V.acc_w$good_bad_slf <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Self_Bad
df.L1.V.acc_w$good_oth <- df.L1.V.acc_w$match_Other_Good - df.L1.V.acc_w$match_Other_Bad
df.L1.V.acc_w$slf_oth_good <- df.L1.V.acc_w$match_Self_Good - df.L1.V.acc_w$match_Other_Good
df.L1.V.acc_w$slf_oth_bad <- df.L1.V.acc_w$match_Self_Bad - df.L1.V.acc_w$match_Other_Bad

colnames(df.L1.V.acc_w) <- paste("L_acc", colnames(df.L1.V.acc_w), sep = "_")
colnames(df.L1.V.acc_w)[colnames(df.L1.V.acc_w) == 'L_acc_Subject'] <- 'Subject'
write.csv(df.L1.V.acc_w,"data_matching_v_acc.csv",row.names=FALSE)
##### save data for later analysis ####

@@

e7_L.p_dprime1 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3,width = .6) +    # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'self-referential',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme  + 
        theme(axis.text = element_text (size = 24,color = 'black')) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good   ","Bad"))+
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

e7_L.p_dprime2 <- ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
                      #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        apatheme + 
        theme(axis.text = element_text (size = 24,color = 'black')) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other"))+
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))
# save the plot to pdf file
ggsave("e7_L.p_dprime2.pdf", e7_L.p_dprime2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")

@@

```{r plot1 the d prime_e7_match, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Identity, group = Morality,shape = Morality, fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = 1,     # width of the error bar
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'self-referential',y = 'd prime') +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        apatheme + 
        theme(axis.text = element_text (size = 24,color = 'black')) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce between title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good    ","Bad")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

@@

```{r plot2 the d prime_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
ggplot(data = df.L1.V.SDT.sum,aes(y = dprime, x = Morality, group = Identity,shape = Identity, fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = dprime - se, ymax = dprime + se),
        #geom_errorbar(aes(ymin = 1, ymax = 4),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        labs(x = 'Moral valence',y = 'd prime') +
        #ylab(" Reaction times") + 
        #ylim(1, 4) +
        ggtitle("d prime for each condition") +
        coord_cartesian(ylim=c(1,3.5))+
        scale_y_continuous(breaks = seq(1,3.5,0.5),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter. 
        #theme_classic()
        apatheme + 
        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other"))+
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

@@

##### save the rt data for late used ####
colnames(df.L1.V.RT.subj_w) <- paste("L_rt", colnames(df.L1.V.RT.subj_w), sep = "_")
colnames(df.L1.V.RT.subj_w)[colnames(df.L1.V.RT.subj_w) == 'L_rt_Subject'] <- 'Subject'
write.csv(df.L1.V.RT.subj_w,"data_matching_v_RT.csv",row.names=FALSE)
#### save the rt data ####

@@

e7_L.p_rt1 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Self-referential") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times (ms)") + 
        apatheme + 
        theme(axis.text    = element_text(size = 24, color = 'black')) + 
        theme(axis.title   = element_text(size = 24)) + 
        theme(plot.title   = element_text(size = 24)) +
        theme(legend.text  = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good   ","Bad")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

e7_L.p_rt2 <- ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +   # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Moral valence") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800))+
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        scale_y_continuous("Reation Times  (ms)",breaks = seq(500,800,50),expand = c(0, 0)) +
        apatheme + 
        theme(axis.text = element_text (size = 24, color = 'black')) + 
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +  # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

ggsave("e7_L.p_rt2.pdf", e7_L.p_rt2, scale = 1,height = 8, width = 8, dpi = 300, family = "Times")

@@

```{r plot2 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
# change a way to plot
ggplot(data = df.L1.V.RT.grand.match, aes(x=Identity,y=RT,group=Morality,shape = Morality,fill = Morality)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) +  # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Self-referential") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800)) +
        scale_y_continuous(breaks=seq(500,800,50),expand = c(0, 0)) +
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        #scale_y_continuous("Reation Times (ms)") + 
        apatheme + 
        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("Good    ","Bad"))+
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))

@@

```{r plot1 the RT_e7_L, fig.width=4, fig.height=6,echo=FALSE,warning=FALSE,message=FALSE }
# df.L1.V.RT.grand.match <- df.L1.V.RT.grand[df.L1.V.RT.grand$Matchness == "match",]
ggplot(data = df.L1.V.RT.grand.match, aes(x=Morality,y=RT,group=Identity,shape = Identity,fill = Identity)) +
        geom_bar(position = position_dodge(),stat = "identity",colour = "black", size=.3, width = 0.6) + # Thinner lines
        geom_errorbar(aes(ymin = RT-se, ymax = RT + se),
                      size = 1,
                      width = .2,
                      position=position_dodge(.6)) +
        xlab("Moral valence") +
        ylab(" Reaction times (ms)") + 
        coord_cartesian(ylim=c(500,800))+
        scale_fill_grey (start=0.2, end=0.8) +   # using grey scale, start from darker, end to lighter.
        #ylim(0.3, 0.8) +
        ggtitle("RT for each condition") +
        scale_y_continuous("Reation Times  (ms)",expand = c(0, 0)) + 
        apatheme + 
        theme(axis.text = element_text (size = 24,color = 'black')) +   # set the font size and color of the axis title
        theme(axis.title = element_text (size = 24)) + 
        theme(plot.title = element_text(size = 24)) +
        theme(legend.text = element_text(size =24)) +
        theme(axis.title.y = element_text(margin=margin(0,20,0,0))) +   # increase the space between title and y axis
        theme(axis.title.x = element_text(margin=margin(20,0,0,0))) +   # increase the sapce betwen title and x axis
        scale_fill_manual(values=c("grey20", "grey80"),labels=c("self    ","other")) +
        theme(axis.line.x = element_line(color="black", size = 1),
        axis.line.y = element_line(color="black", size = 1))
